Bow shocks, bow waves, and dust waves. IV. Bow shape statistics

### 2019-04-02 papers/Papers1234/sec-observational-diagnostics.tex
Remove the figure about K18 interpolation error from Paper III
Requested by Chip Kobulnicky

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
  \caption{Discrepancies in \SI{70}{\um} emissivities that we have
    identified in K18.  Red crosses show the emissivities given in
    K18's Table~2 as a function of the radiation field \(U\), while
    the solid gray line shows the emissivities that they claim to be
    using from \citet{Draine:2007a}.  The dashed line shows the
    emissivities that we believe they should have been using, which
    correct for the marked difference in spectral energy distribution
    between OB stars and the Galactic interstellar radiation field
    (see \S~\ref{sec:grain-temp-emiss}).}
  \label{fig:k18-emissivity}
\end{figure}

@@

In principle, both methods are valid and their different assumptions
and dependencies on observed quantities and auxiliary parameters
provide an important cross check on one another.  However, as
explained in detail in \S~\ref{sec:grain-temp-emiss}, the \(j_\nu(U)\)
relation depends on the shape of the illuminating SED, which means
that the \citet{Draine:2007a} models require modification when applied
to grains around OB stars.  In addition, when attempting to replicate
the K18 values of \(j_{70}\) we find that they only follow the
\citet{Draine:2007a} values for \(U > \num{e4}\), tending to a
constant value for weaker radiation fields.  The situation is
summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
directly from Table~2 of K18 are shown by red crosses, the values they
claim to be using are shown by the gray solid line (this curve is
consistent with that shown in K18 Fig.~2), and the values they
\textit{should} have been using are shown by the gray dashed
line. Note that this correction may also resolve the color temperature
discrepancy noted by \citet{Kobulnicky:2017a}.

% If we replaced K3 with M3, then mass loss rates would be reduced by 1.86 across the board

@@

After correcting the \SI{70}{\um} emissivities in this way, we
re-derive the mass loss rates, following the same steps as in K18,
which are then used in Figure~\ref{fig:mass-loss-vs-luminosity}b
above.  The difference between these corrected mass-loss rates and
those published in K18 is shown in
Figure~\ref{fig:k18-mdot-corrected-emissivity}.  It can be seen that
sources with \(U \approx \num{e3}\) (darker shading) are relatively
unaffected but that sources with stronger radiation fields (lighter
shading) have their mass-loss increasingly reduced, as could be
surmised from Figure~\ref{fig:k18-emissivity}.  The average reduction
is by a factor of about two.

>>>>

% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figs/K18-emissivity-vs-U}
%   \caption{Discrepancies in \SI{70}{\um} emissivities that we have
%     identified in K18.  Red crosses show the emissivities given in
%     K18's Table~2 as a function of the radiation field \(U\), while
%     the solid gray line shows the emissivities that they claim to be
%     using from \citet{Draine:2007a}.  The dashed line shows the
%     emissivities that we believe they should have been using, which
%     correct for the marked difference in spectral energy distribution
%     between OB stars and the Galactic interstellar radiation field
%     (see \S~\ref{sec:grain-temp-emiss}).}
%   \label{fig:k18-emissivity}
% \end{figure}

@@

In principle, both methods are valid and their different assumptions
and dependencies on observed quantities and auxiliary parameters
provide an important cross check on one another.  However, as
explained in detail in \S~\ref{sec:grain-temp-emiss}, the \(j_\nu(U)\)
relation depends on the shape of the illuminating SED, which means
that the \citet{Draine:2007a} models require modification when applied
to grains around OB stars.  A further discrepancy arises due to an
interpolation error in K18, which resulted in values of \(j_{70}\)
being overestimated by about a factor of 2 for sources with weak
radiation fields (H.~Kobulnicky, priv.~comm.).

% In addition, when attempting to replicate
% the K18 values of \(j_{70}\) we find that they only follow the
% \citet{Draine:2007a} values for \(U > \num{e4}\), tending to a
% constant value for weaker radiation fields.

% The situation is
% summarized in Figure~\ref{fig:k18-emissivity}, where the values taken
% directly from Table~2 of K18 are shown by red crosses, the values they
% claim to be using are shown by the gray solid line (this curve is
% consistent with that shown in K18 Fig.~2), and the values they
% \textit{should} have been using are shown by the gray dashed
% line. Note that this correction may also resolve the color temperature
% discrepancy noted by \citet{Kobulnicky:2017a}.

@@

After correcting the \SI{70}{\um} emissivities in this way, we
re-derive the mass loss rates, following the same steps as in K18,
which are then used in Figure~\ref{fig:mass-loss-vs-luminosity}b
above.  The difference between these corrected mass-loss rates and
those published in K18 is shown in
Figure~\ref{fig:k18-mdot-corrected-emissivity}.  It can be seen that
sources with \(U \approx \num{e3}\) (darker shading) are relatively
unaffected but that sources with stronger radiation fields (lighter
shading) have their mass-loss increasingly reduced.
% , as could be
% surmised from Figure~\ref{fig:k18-emissivity}.
The average reduction is by a factor of about two.
